Review of Assigned Readings

### 2018-01-04 paper/paper.tex
Update paper.tex
grammar

This model shows that the current value of our endogenous variables is determined by its own past values, the past values of the other variable and an error term. The second equation is directly relevant to our research question, as it allows to look into the correlation between present bitcoin price and past tweet count.\\

>>>>

This model shows that the current value of our endogenous variables is determined by its own past values, the past values of the other variable and an error term. The second equation is directly relevant to our research question, as it allows to look into the correlation between the present bitcoin price and the past tweet count.\\
